Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-06-10 paper/paper.tex
#23 clarify aggregation description

I also build coarsened versions of this dataset in which I aggregate years into longer periods. Apart from the yearly version there is also a 10-yearly version, a 50-yearly version and a 100-yearly version. Not only does this make event studies nicer to look at, it also allows me to use more of the conflict and construction data: the 50-year and 100-year versions contain events that aren't recorded with a precise year, but only "beginning of the 16th century" and the like.

>>>>

I also build coarsened versions of this dataset in which I aggregate years into longer periods (10, 50, and 100 years). Not only does this aggregation make event studies nicer to look at, it also allows me to use more of the conflict and construction data as periods get longer: the 50-year and 100-year versions contain events that aren't recorded with a precise year, but only "beginning of the 16th century" and the like. While the 1-year and 10-year data builds contain BLANK construction events with sufficiently precise timing, the 50-year version contains BLANK and the 100-year version contains BLANK.
